---
title: "Extending material"
author: "Lingyu Meng"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, echo=FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo=FALSE)
library("tidyverse")
library("cowplot")
colorset_1 <- c("#9FD2CD", "#76C3D2", "#165D95", "#3E377E", "#662B77") # Colours of Sheffield row 5
colorset_2 <- c("#A3CFAD", "#54AF7A", "#447E5D", "#668136", "#36532C") # Colours of Sheffield row 6
```

# Expected results

## Conditions

I supposed that losing condition will lead to more direct exploration. That will yield a result that higher w2 in losing condition than in wining condition.

However, I am not really sure about whether we should suppose it, especially, when we control the risk aversion. It has a fair chance that the framing effect (wining/losing condition) have nothing to do with exploration.

```{r simulation of condition}
V <- seq(-6, 6, 0.01)
Win <- pnorm(V + 0.5 + V/ 1.72) # 1.72 is the standard deviation of the population (TU)
Loss <- pnorm(V + 1 + V/ 1.72)
data_win_loss <- data.frame(V, Win, Loss) %>% 
  gather(key = "condition", value = "P", -V)

SR <- pnorm(V + 0.5 + V/ 1.72)
rR <- pnorm(V + V/ 1.89) # 1.89 is the standard deviation of the population (TU)
data_SR_rR <- data.frame(V, SR, rR) %>% 
  gather(key = "condition", value = "P", -V)
```

```{r figure of win}
win_loss <- ggplot(data_win_loss, aes(x = V, y = P, linetype = condition)) +
  geom_line(linewidth = 1) +
  labs(x = "Expected value difference V(1) - V(2)",
       y = "Choice Probability P(1)",
       title = "Hypothetical result of winning and losing condition") +
  theme_cowplot() +
  theme(legend.position = c(0.05, 0.9))
win_loss
```

As previous study found that the relative risk in RR condition will be close to 0, I supposed there will be a different intercept between SR and rR condition. The TU is set to the real value of variance in the population. Based on the definition of TU: $TU=\sqrt{(\sigma_1^2+\sigma_2^2)}$, in our experiment, the TU in SR is

```{r calculation of TU, echo=TRUE}
r <- c(-1,-1,-1,0,0,0,0,0,0,1,1,1)
R <- c(1,2,3,3,4,4,4,4,5,5,6,7)
V_r <- var(r) * 12/11 # using the variance of the population instead of the unbiased estimator
V_R <- var(R) * 12/11
sqrt(V_R + 0)
```

Whereas the TU in rR is

```{r, echo=TRUE}
sqrt(V_r + V_R)
```

Those are not real TU, as the TU should be estimated during subjects' decision making. However, it is a little bit tricky to explain the setting. We may need to discuss it later. For now, I will use the real value of variance in the population in the following simulation.

I setted same w3 for rR and SR. However, the slop is different due to the different TU.

```{r figure of rR}
SR_rR <- ggplot(data_SR_rR, aes(x = V, y = P, colour = condition)) +
  geom_line(linewidth = 1) +
  labs(x = "Expected value difference V(1) - V(2)",
       y = "Choice Probability P(1)",
       title = "Hypothetical result of SR and rR condition") +
  theme_cowplot() +
  theme(legend.position = c(0.05, 0.9))
SR_rR
```

# Individual difference

## Intolerance of Uncertaint (IU)

H1: High IU lead to less direct exploration

```{r simulation of IU, echo=FALSE}
Low <- pnorm(V + 1 + V/ 1.72)
Low_M <- pnorm(V + 0.8 + V/ 1.72)
Medium <- pnorm(V + 0.5 + V/ 1.72)
Medium_H <- pnorm(V + 0.3 + V/ 1.72)
High <- pnorm(V + 0.1 + V/ 1.72)
levels = c("Low", "Low_M", "Medium", "Medium_H", "High")
labs = c("Low", "Low to medium", "Medium", "Medium to high", "High")

data_H1 <- data.frame(V, Low, Low_M, Medium, Medium_H, High) %>% 
  gather(key = "IU level", value = "P", -V) %>% 
  mutate(`IU level` = factor(`IU level`, levels = levels, labels = labs))
```

```{r figure of H1}
H1 <- ggplot(data_H1, aes(x = V, y = P , colour = `IU level`)) +
  geom_line() +
  labs(x = "Expected value difference V(1) - V(2)",
       y = "Choice Probability P(1)",
       title = "Hypothetical result of IU level") +
  scale_colour_manual(values = colorset_1) +
  theme_cowplot() +
  theme(legend.position = c(0.05, 0.8))
H1
```

## Impulsiveness (IM)

H2: High IM will lead to more random exploration

Notice: the sum of $w_1$ and $w_3$ is 2.

This two items should be and actually are negative correlated with each other (Fan et al., 2023).

```{r simulation of IM, echo=FALSE}
Low <- pnorm(0.8 * V + 0.5 + 1.2 * V/ 1.72)
Low_M <- pnorm(0.4 * V + 0.5 + 1.6 * V/ 1.72)
Medium <- pnorm(0 * V + 0.5 + 2 * V/ 1.72)
Medium_H <- pnorm(-0.4 * V + 0.5 + 2.4 * V/ 1.72)
High <- pnorm(-0.8 * V + 0.5 + 2.8 * V/ 1.72)
levels = c("Low", "Low_M", "Medium", "Medium_H", "High")
labs = c("Low", "Low to medium", "Medium", "Medium to high", "High")

data_H2 <- data.frame(V, Low, Low_M, Medium, Medium_H, High) %>% 
  gather(key = "IM level", value = "P", -V) %>% 
  mutate(`IM level` = factor(`IM level`, levels = levels, labels = labs))
```

```{r figure of H2}
H2 <- ggplot(data_H2, aes(x = V, y = P , colour = `IM level`)) +
  geom_line() +
  labs(x = "Expected value difference V(1) - V(2)",
       y = "Choice Probability P(1)",
       title = "Hypothetical result of IM level") +
  scale_colour_manual(values = colorset_2) +
  theme_cowplot() +
  theme(legend.position = c(0.05, 0.8))
H2
```

# Interactions

## IU x Win/Loss

H3: In loss condition, participates with lower IU will show a similar level of direct exploration compared to participates with higher IU. In win condition, participates with lower IU will show a greater increase in direct exploration compared to participates with higher IU.

Although I lake of the evidence to support the hypothesis of framing effect, there are some evidence support the interaction between IU and win/loss condition. As the IU is supposed to show overestimation of the probability of negative events, the losing condition will lead to more direct exploration.

```{r simulation of IU x Loss, echo=FALSE}
w2_LW <- 0.6
w2_HW <- 0.4
w2_LL <- 1
w2_HL <- 0.5
Low_Win <- pnorm(V + w2_LW + V/ 1.72)
Low_Loss <- pnorm(V + w2_LL + V/ 1.72)
High_Win <- pnorm(V + w2_HW + V/ 1.72)
High_Loss <- pnorm(V + w2_HL + V/ 1.72)
data_H3 <- data.frame(V, Low_Win, Low_Loss, High_Win, High_Loss) %>% 
  gather(key = "Condition", value = "P", -V) %>%
  separate(Condition, into = c("IU level", "Condition"), sep = "_") 

data_H3_w2 <- tibble(
  w2 = c(w2_LW, w2_HW, w2_LL, w2_HL),
  Condition = c("Win", "Win", "Loss", "Loss"),
  `IU level` = c("Low", "High", "Low", "High"))
```

```{r figure of H3}
H3 <- ggplot(data_H3, aes(x = V, y = P, colour = `IU level`, linetype = Condition)) +
  geom_line() +
  labs(x = "Expected value difference V(1) - V(2)",
       y = "Choice Probability P(1)",
       title = "Hypothetical result of IU level and win/loss interaction") +
  scale_colour_manual(values = c(colorset_1[[5]], colorset_1[[2]])) +
  theme_cowplot() +
  theme(legend.position = c(0.05, 0.75))
H3
```

```{r figure of H3 in w2}
H3_w2 <- ggplot(data_H3_w2, aes(x = Condition, y = w2, fill = `IU level`)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Win/Loss condition",
       y = "Direct exploration indicated by w2",
       title = "Hypothetical result of IU level and win/loss interaction \nindicated by parameter") +
  theme_cowplot() +
  scale_fill_manual(values = c(colorset_1[[5]], colorset_1[[2]])) +
  theme(legend.position = c(0.05, 0.85))
H3_w2
```

## IM x Win/Loss

H4: In win condition, participates with higher IM will show a small higher random exploration compared to participates with lower IM In loss condition, participates with higher IM will show a greater increase in random exploration compared to participates with lower IM.

```{r simulation of IM x Loss, echo=FALSE}
w3_LW <- 0.7
w3_HW <- 1.7
w3_LL <- 1.2
w3_HL <- 2.7
Low_Win <- pnorm((2 - w3_LW) * V + w3_LW * V/ 1.72)
Low_Loss <- pnorm((2 - w3_LL) * V + w3_LL * V/ 1.72)
High_Win <- pnorm((2 - w3_HW) * V + w3_HW * V/ 1.72)
High_Loss <- pnorm((2 - w3_HL) * V + w3_HL * V/ 1.72)
data_H4 <- data.frame(V, Low_Win, Low_Loss, High_Win, High_Loss) %>% 
  gather(key = "Condition", value = "P", -V) %>%
  separate(Condition, into = c("IM level", "Condition"), sep = "_") 

data_H4_w3 <- tibble(
  w3 = c(w3_LW, w3_HW, w3_LL, w3_HL),
  Condition = c("Win", "Win", "Loss", "Loss"),
  `IM level` = c("Low", "High", "Low", "High"))
```

```{r figure of H4}
H4 <- ggplot(data_H4, aes(x = V, y = P, colour = `IM level`, linetype = Condition)) +
  geom_line() +
  labs(x = "Expected value difference V(1) - V(2)",
       y = "Choice Probability P(1)",
       title = "Hypothetical result of IM level and win/loss interaction") +
  scale_colour_manual(values = c(colorset_2[[5]], colorset_2[[2]])) +
  theme_cowplot() +
  theme(legend.position = c(0.05, 0.75))
H4
```

```{r figure of H4 in w3}
H4_w3 <- ggplot(data_H4_w3, aes(x = Condition, y = w3, fill = `IM level`)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Win/Loss condition",
       y = "Random exploration indicated by w3",
       title = "Hypothetical result of IM level and win/loss interaction \nindicated by parameter") +
  scale_fill_manual(values = c(colorset_2[[5]], colorset_2[[2]])) +
  theme_cowplot() +
  theme(legend.position = c(0.8, 0.85))
H4_w3
```

```{r save figures}
ggsave2("fig/H4.png", H4, width = 7, height = 4)
ggsave2("fig/H4_w3.png", H4_w3, width = 7, height = 4)
ggsave2("fig/H3_w2.png", H3_w2, width = 7, height = 4)
ggsave2("fig/H3.png", H3, width = 7, height = 4)
ggsave2("fig/H2.png", H2, width = 6, height = 4)
ggsave2("fig/H1.png", H1, width = 6, height = 4)
ggsave2("fig/SR_rR.png", SR_rR, width = 6, height = 4)
ggsave2("fig/win_loss.png", win_loss, width = 6, height = 4)
```
